---
title: "RMarkdown Notes"
author: "Ou Zhang"
date: "January 15, 2019"
output: 
    html_document:
        highlight: haddock
        theme: spacelab
        toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r global_function}

knitr::opts_chunk$set(echo = FALSE, 
                      eval = TRUE, 
                      collapse = TRUE,
                      message = FALSE,
                      warning = FALSE, 
                      fig.path = "Figures/",
                      fig.width = 12, 
                      fig.height = 8,
                      fig.aligh = "center")

```
# Reproducible reporting

## Knitr Ninja from Yihui Xie

* Avoid Copy + Paste  
* Automation  
* Dynamic documents  
 - code + narrative = report  
  (computing languages + authoring languages)  

**************************************************

## Packrat A dependency Management System for R  

Packrat is an R package that helps you manage your project's R package
  dependencies in a way that is:
  
  - Reproducible  
    Records the exact package versions you depend on, and ensures those exact versions are the onece that get installed wherever you go.
    
  - Isolated  
    Installing a new or updated package for one project won't break your other projects, and vice versa.  

  - Portable  
  easily transport your projects from one computer to another, even across different platforms. 

### Main Packrat Verbs  

  - The snapshot of your project's R dependencies  
  
  - The private library powering your project.  
  
    `**packrat::snapshot()** records the package versions used by a project and downloads the source code for storage with the project`  
    
    `**packrat::restore()** applies the previous snapthos to a directory`    
    
### bundle and unbundle packages

packrat is only availabe on github.com not on cran.
    

# Interactive Reporting from Joe Chang and Garrett Grolemund
  

## Shiny: R made interactive - Joe Cheng

Just some simple Shiny introduction.

## Embedding Shiny Apps in R Markdown documents - Garrett Grolemund


* Add R chunk to the markdown.

### A widget for .Rmd

`library(rmdexamples)`  
`Kmeans_cluster(iris)`

### The easist way to use Shiny

1. Works for ggvis.









  

 